---
title: "Project proposal"
author: "Data Pirates"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(here)
```


## 1. Introduction


The dataset that we have decided to analyse for this project is called ‘Countries of the world’. 

In this project we aim to research the relationships between various geographical and societal qualities across the different countries.

There are 20 variables in this dataset, which include:
`country`, `region`, `population`, `area`, `pop_density`, `coastline `, `net_migration`, `infant_mortality`, `GDP`, `literacy`, `phones`, `arable`, `crops`, `other`, `climate`, `birthrate`, `deathrate`, `agriculture`, `industry` and `service`.

Of these 20 variables: `country` and `region` are string variables, `area`, `pop_density` and `GDP` are integer variables, and the rest are decimal variables. 

Each observation represents different physical/geographical and societal attributes of each country in the dataset. There are 227 observations in total.

This data set has information about the different countries between 1970 and 2017. It is made up of data from the US government specifically the CIA World Factbook. We obtained this data from https://www.kaggle.com/fernandol/countries-of-the-world.  


## 2. Data

``` {r load-data, echo=FALSE}
Countries_of_the_world <- read_csv(here :: here("data/countries of the world.csv"))

```

Uploaded the dataset in data folder. There is a total of 227 observations and 20 variables in this dataset.

## 3. Data analysis plan

Our outcome is quality of life, and this will be based on a few variables - `literacy`, `GDP`, `infant_mortality`, `death_rate`... Our predictor will also be based on a few seperate variables - `net_migration`, `pop_ density`, `climate`, `arable`...

``` {r rename-variables, echo=FALSE}
Countries_of_the_world <- Countries_of_the_world %>%
  rename(
      country = Country,
      region = Region,
      population = Population,
      area = `Area (sq. mi.)`,
      pop_density = `Pop. Density (per sq. mi.)`,
      coastline = `Coastline (coast/area ratio)`,
      net_migration = `Net migration`,
      infant_mortality = `Infant mortality (per 1000 births)`,
      GDP = `GDP ($ per capita)`,
      literacy = `Literacy (%)`,
      phones = `Phones (per 1000)`,
      arable = `Arable (%)`,
      crops = `Crops (%)`,
      other = `Other (%)`,
      climate = Climate,
      birthrate = Birthrate,
      deathrate = Deathrate,
      agriculture = Agriculture,
      industry = Industry,
      service = Service
    ) 
```

We should expect to use a variety of inferential statistical methods, mainly correlation and regression analysis.

Our hypothesized answer is that there would be at least a weak relation between quality of life and other qualities of the country, therefore results that show some correlation between variables would support our hypothesis.

```{r intro-statistics}
intro_statistics_1 <- Countries_of_the_world %>%
  select(region, infant_mortality, GDP) %>%
  arrange(desc(GDP))
intro_statistics_1

Countries_of_the_world %>%
  ggplot(aes(x = GDP, y = infant_mortality)) +
  geom_point() + 
  labs(
    x = "GDP Per Capita",
    y = "Infant Mortality Per 1000"
  )


```

As shown in the graph usually as the GDP Per Capita goes up the infant mortality goes down. 

```{r}

```



