---
title: <font size='10'>Relationship between geographical and societal qualities</font>
subtitle: <font size='8'> Of countries in the world</font>
author: <font size='6'> Data Pirates <br> Hamish, Sara, Li Shiyao</font>
institute: <font size='6'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
library(gganimate)
library(reshape2)
library(patchwork)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
Cotw <- read_csv(here :: here("data/countries of the world.csv"))
```

```{r rename-variables, echo = FALSE}
Cotw <- Cotw %>%
  rename(
      country = Country,
      region = Region,
      population = Population,
      area = `Area (sq. mi.)`,
      pop_density = `Pop. Density (per sq. mi.)`,
      coastline = `Coastline (coast/area ratio)`,
      net_migration = `Net migration`,
      infant_mortality = `Infant mortality (per 1000 births)`,
      GDP = `GDP ($ per capita)`,
      literacy = `Literacy (%)`,
      phones = `Phones (per 1000)`,
      arable = `Arable (%)`,
      crops = `Crops (%)`,
      other = `Other (%)`,
      climate = Climate,
      birthrate = Birthrate,
      deathrate = Deathrate,
      agriculture = Agriculture,
      industry = Industry,
      service = Service
    ) 
  
```


# What is the relationship between geographical, economic and societal qualities in countries all over the world? 

# To break this question down, we're going to look at 3 specific areas -
1. How strong is the correlation between economic and societal qualities
2. How impactful are geographical qualities on the development of societal qualities
3. What is the relationship between geographical qualities and economic qualities

# Linear Regression analysis

```{r regression, echo = FALSE, include = FALSE}

infant_mortality_vs_GDP <- lm(GDP ~ deathrate + infant_mortality , data = Cotw) 
tidy(infant_mortality_vs_GDP)
glance(infant_mortality_vs_GDP) 
linear_reg() %>%
 set_engine("lm") %>%
  fit(log(GDP) ~ deathrate+infant_mortality , data = Cotw) %>%
  tidy() 
```

Linear equation...
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
How does the deathrate and infant_mortality affect GDP$$\log(GDP)=9.07 + 0.0746* deathrate - 0.0333* infant mortality$$
~~~~~~~~~~~~~~NEED TO FIX~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


# Economic sectors vs Location

```{r continent-tidy, echo = FALSE}
Cotw <- Cotw %>%
  mutate(continent = case_when(region == "ASIA (EX. NEAR EAST)" ~ "Asia",
                               region == "NEAR EAST" ~ "Asia",
                               region == "C.W. OF IND. STATES" ~ "Asia",
                               region == "WESTERN EUROPE" ~ "Europe",
                               region == "BALTICS" ~ "Europe",
                               region == "EASTERN EUROPE" ~ "Europe", 
                               region == "LATIN AMER. & CARIB" ~ "South and Central America",
                               region == "NORTHERN AMERICA" ~ "North America",
                               region == "OCEANIA" ~ "Oceania",
                               region == "SUB-SAHARAN AFRICA" ~ "Africa",
                               region == "NORTHERN AFRICA" ~ "Africa"))
```

```{r continent-vs-sector, echo = FALSE}
cotwspe <- Cotw %>%
  select(continent, agriculture, service, industry) %>% 
  group_by(continent) %>%
  mutate(meanagr = mean(agriculture, na.rm = TRUE)) %>%
  mutate(meanser = mean(service, na.rm = TRUE)) %>%
  mutate(meanind = mean(industry, na.rm = TRUE)) %>%
  select(continent, meanagr, meanind, meanser) %>%
  melt(id.vars = "continent") 
  
ggplot(unique(cotwspe), aes(x = value, y = continent, fill = variable)) + 
  geom_bar(stat = "identity") +
  labs(
    title = "Difference in economic qualities (sectors)",
    subtitle = "depending on the continent",
    x = "Value",
    y = "Continent",
    fill = "Variable"
    ) +
  scale_fill_discrete(labels = c("Agriculture", "Industry", "Service"))

```

## Plot and text

```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
p1 <- Cotw %>%
  ggplot(aes(x = phones, y = service, color = continent)) +
  geom_point(alpha = 1) +
  geom_smooth(inherit.aes = FALSE, aes(x = phones, y = service), method = "lm", se = FALSE) +
  ylim(0,1) +
  theme(legend.title = element_blank(),
        legend.text = element_blank(),
        legend.position = "none",
        plot.title = element_text(size = rel(0.9))) +
  labs(title="Phones per 1000 vs. service",
       x = "Phones per 1000",
       y = "Service")
  
p2 <- Cotw %>%
  ggplot(aes(x = GDP, y = service, color = continent)) +
  geom_point(alpha = 1) +
  geom_smooth(inherit.aes = FALSE, aes(x = GDP, y = service), method = "lm", se = FALSE) +
  ylim(0,1) +
  theme(axis.title.y = element_blank(),
        axis.text = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = rel(0.9))) +
  labs(title="GDP per Capita vs. service",
       x = "GDP per Capita",
       y = "Service",
       colour = "Continent")
p1 + p2
```


# Table

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
#kable(head(data = Cotw, select(continent, population)), format = "html")
```

# To conclude {data-background-image="img/world-map.gif"}

# Thank you for listening :)


Hamish - 2 plots + fix, edit write-up, regression
Sara - introduction of write up (done), essay plan (done), labs and table (continent and related descriptive columns), background theme
Yuki - conclusion, labs, make a plot


