---
title: Relationship between geographical and societal qualities
subtitle: <font size='6'> Of countries in the world</font>
author: <font size='8'> Data_Pirates <br> Hamish, Sara, Li Shiyao</font>
institute: <font size='10'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
library(gganimate)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
Countries_of_the_world <- read_csv(here :: here("data/countries of the world.csv"))
```


# The question we wanted to answer during this project was whether there was a relationship between geographical and societal qualities in countries all over the world. {data-background-image="img/confetti.jpg"} 

# regression analysis (main)

```{r boring-regression, echo = FALSE}
# a boring regression
```

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs (\$...\$), e.g. $\alpha+\beta$. You can use the display style with double dollar signs:

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
# other statistical methods used

# Plots

```{r rename-variables, echo = FALSE}
Countries_of_the_world <- Countries_of_the_world %>%
  rename(
      country = Country,
      region = Region,
      population = Population,
      area = `Area (sq. mi.)`,
      pop_density = `Pop. Density (per sq. mi.)`,
      coastline = `Coastline (coast/area ratio)`,
      net_migration = `Net migration`,
      infant_mortality = `Infant mortality (per 1000 births)`,
      GDP = `GDP ($ per capita)`,
      literacy = `Literacy (%)`,
      phones = `Phones (per 1000)`,
      arable = `Arable (%)`,
      crops = `Crops (%)`,
      other = `Other (%)`,
      climate = Climate,
      birthrate = Birthrate,
      deathrate = Deathrate,
      agriculture = Agriculture,
      industry = Industry,
      service = Service
    ) 
  
```

```{r coastal_or_not, echo = FALSE}
Countries_of_the_world %>%
  mutate(coastal = if_else(coastline == 0, FALSE, TRUE)) %>%
  ggplot(aes(x = GDP, colour = coastal)) +
  geom_density()
  
```

## Plot and text

::: columns
:::: column
* Some text
* goes here
::::

:::: column
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

## Different widths

::: columns
:::: {.column width="40%"}
* Some text
* goes here
::::

:::: {.column width="60%"}
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

# Table

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("")
```

Or you can also include a full page image. See next slide.

## {data-background-image="https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80"}



