---
title: <font size='10'>Relationship between geographical, economic and societal qualities</font>
subtitle: <font size='8'> Of countries in the world</font>
author: <font size='6'> Data Pirates <br> Hamish, Sara, Li Shiyao</font>
institute: <font size='6'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    theme: sky
    center: true
    self_contained: false
    transition: fade
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
library(gganimate)
library(reshape2)
library(patchwork)
library(magrittr)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
Cotw <- read_csv(here :: here("data/countries of the world.csv"))
```

```{r rename-variables, echo = FALSE}
Cotw <- Cotw %>%
  rename(
      country = Country,
      region = Region,
      population = Population,
      area = `Area (sq. mi.)`,
      pop_density = `Pop. Density (per sq. mi.)`,
      coastline = `Coastline (coast/area ratio)`,
      net_migration = `Net migration`,
      infant_mortality = `Infant mortality (per 1000 births)`,
      GDP = `GDP ($ per capita)`,
      literacy = `Literacy (%)`,
      phones = `Phones (per 1000)`,
      arable = `Arable (%)`,
      crops = `Crops (%)`,
      other = `Other (%)`,
      climate = Climate,
      birthrate = Birthrate,
      deathrate = Deathrate,
      agriculture = Agriculture,
      industry = Industry,
      service = Service
    ) 
  
```


# What is the relationship between geographical, economic and societal qualities in countries all over the world? 

#
1. How strong is the correlation between economic and societal qualities? 
2. How impactful are geographical qualities on the development of economic or societal qualities?


# Linear Regression analysis

```{r regression, echo = FALSE, include = FALSE}

infant_mortality_vs_GDP <- lm(GDP ~ deathrate + infant_mortality + phones, data = Cotw) 
tidy(infant_mortality_vs_GDP)
glance(infant_mortality_vs_GDP) 
linear_reg() %>%
 set_engine("lm") %>%
  fit(log(GDP) ~ deathrate+infant_mortality+phones , data = Cotw) %>%
  tidy() 
```



Linear equation...
<font size='4'>$$\log(GDP)=8.32 + 0.035* deathrate - 0.0186* infantmortality + 0.00255*phones$$</font>



# Economic sectors vs Location

```{r continent-tidy, echo = FALSE}
Cotw <- Cotw %>%
  mutate(continent = case_when(region == "ASIA (EX. NEAR EAST)" ~ "Asia",
                               region == "NEAR EAST" ~ "Asia",
                               region == "C.W. OF IND. STATES" ~ "Asia",
                               region == "WESTERN EUROPE" ~ "Europe",
                               region == "BALTICS" ~ "Europe",
                               region == "EASTERN EUROPE" ~ "Europe", 
                               region == "LATIN AMER. & CARIB" ~ "South and Central America",
                               region == "NORTHERN AMERICA" ~ "North America",
                               region == "OCEANIA" ~ "Oceania",
                               region == "SUB-SAHARAN AFRICA" ~ "Africa",
                               region == "NORTHERN AFRICA" ~ "Africa"))
```

```{r continent-vs-sector, echo = FALSE}
cotwspe <- Cotw %>%
  select(continent, agriculture, service, industry) %>% 
  group_by(continent) %>%
  mutate(meanagr = mean(agriculture, na.rm = TRUE)) %>%
  mutate(meanser = mean(service, na.rm = TRUE)) %>%
  mutate(meanind = mean(industry, na.rm = TRUE)) %>%
  select(continent, meanagr, meanind, meanser) %>%
  melt(id.vars = "continent") 
  
ggplot(unique(cotwspe), aes(x = value, y = continent, fill = variable)) + 
  geom_bar(stat = "identity") +
  labs(
    title = "Difference in economic qualities (sectors)",
    subtitle = "depending on the continent",
    x = "Value",
    y = "Continent",
    fill = "Variable"
    ) +
  scale_fill_discrete(labels = c("Agriculture", "Industry", "Service"))

```

## 

```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
Cotw %>%
  ggplot(aes(x = GDP, y = service, color = continent)) +
  geom_point(alpha = 1) +
  geom_smooth(inherit.aes = FALSE, aes(x = GDP, y = service), method = "lm", se = FALSE) +
  guides(color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.title = element_text(size  = rel(0.8)),
        legend.text = element_text(size = rel(0.6))) +
  labs(title = "GDP per Capita vs. service",
       x = "GDP per Capita",
       y = "Service",
       colour = "Continent")
```

##

```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
Cotw %>%
  ggplot(aes(x = arable, y = GDP, color = continent)) +
  geom_point() +
  geom_smooth(inherit.aes = FALSE, aes(x = arable, y = GDP), method = "lm", se = FALSE) +
    guides(color = guide_legend(override.aes = list(size = 0.4))) + 
  theme(legend.title = element_text(size  = rel(0.8)),
        legend.text = element_text(size = rel(0.6))) +
  labs(title = "GDP per Capita vs. Arable",
       x = "Arable",
       y = "GDP per Capita",
       colour = "Continent")
```

# To conclude {data-background-image="img/world-map.gif"}

