---
title: <font size='10'>Relationship between geographical and societal qualities</font>
subtitle: <font size='8'> Of countries in the world</font>
author: <font size='6'> Data Pirates <br> Hamish, Sara, Li Shiyao</font>
institute: <font size='6'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
library(gganimate)
library(reshape2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
Cotw <- read_csv(here :: here("data/countries of the world.csv"))
```

```{r rename-variables, echo = FALSE}
Cotw <- Cotw %>%
  rename(
      country = Country,
      region = Region,
      population = Population,
      area = `Area (sq. mi.)`,
      pop_density = `Pop. Density (per sq. mi.)`,
      coastline = `Coastline (coast/area ratio)`,
      net_migration = `Net migration`,
      infant_mortality = `Infant mortality (per 1000 births)`,
      GDP = `GDP ($ per capita)`,
      literacy = `Literacy (%)`,
      phones = `Phones (per 1000)`,
      arable = `Arable (%)`,
      crops = `Crops (%)`,
      other = `Other (%)`,
      climate = Climate,
      birthrate = Birthrate,
      deathrate = Deathrate,
      agriculture = Agriculture,
      industry = Industry,
      service = Service
    ) 
  
```


# What is the relationship between geographical, economic and societal qualities in countries all over the world? 

# To break this question down, we're going to look at 3 specific areas -
1. How strong is the correlation between economic and societal qualities
2. How impactful are geographical qualities on the development of societal qualities
3. What is the relationship between geographical qualities and economic qualities

# (linear or logistic) Regression analysis

```{r regression, echo = FALSE}
infant_mortality_vs_GDP <- lm(GDP ~ deathrate+infant_mortality , data = Cotwre)
tidy(infant_mortality_vs_GDP)
glance(infant_mortality_vs_GDP)
linear_reg() %>%
  set_engine("lm") %>%
  fit(log(GDP) ~ deathrate+infant_mortality , data =Cotw) %>%
  tidy()
```

linear equation...
log(GDP)=9.07 + 0.0746* deathrate - 0.0333* infant_mortality
You can write LaTeX math expressions inside a pair of dollar signs (\$...\$), e.g. $\alpha+\beta$. You can use the display style with double dollar signs:

$$\log(GDP)=9.07 + 0.0746* deathrate - 0.0333* infant mortality$$


# Other statistical methods used

```{r stat-method, echo = FALSE}
#show other type of statistical method.
#could use highlight function in order to highlight specific parts of the code
```

# Coastline vs GDP

```{r coastal_or_not, warning=FALSE, echo = FALSE}
Cotw %>%
  mutate(coastal = if_else(coastline == 0, FALSE, TRUE)) %>%
  ggplot(aes(x = GDP, colour = coastal)) +
  geom_density() +
  labs(title = "Relationship between GDP per capita and if the country is bordered by the ocean",
       x = "GDP per capita",
       y = "Density",
       colour = "Coastal")
  
```

description of what is happening in the graph and what it shows and why we chose these variables can be added to write up and explained in presentation

# Economic sectors vs Location

```{r continent-tidy, echo = FALSE}
Cotw <- Cotw %>%
  mutate(continent = case_when(region == "ASIA (EX. NEAR EAST)" ~ "Asia",
                               region == "NEAR EAST" ~ "Asia",
                               region == "C.W. OF IND. STATES" ~ "Asia",
                               region == "WESTERN EUROPE" ~ "Europe",
                               region == "BALTICS" ~ "Europe",
                               region == "EASTERN EUROPE" ~ "Europe", 
                               region == "LATIN AMER. & CARIB" ~ "South America",
                               region == "NORTHERN AMERICA" ~ "North America",
                               region == "OCEANIA" ~ "Oceania",
                               region == "SUB-SAHARAN AFRICA" ~ "Africa",
                               region == "NORTHERN AFRICA" ~ "Africa"))
```

```{r continent-vs-sector, echo = FALSE}
cotwspe <- Cotw %>%
  select(continent, agriculture, service, industry) %>% 
  group_by(continent) %>%
  mutate(meanagr = mean(agriculture, na.rm = TRUE)) %>%
  mutate(meanser = mean(service, na.rm = TRUE)) %>%
  mutate(meanind = mean(industry, na.rm = TRUE)) %>%
  select(continent, meanagr, meanind, meanser) %>%
  melt(id.vars="continent") 
  
ggplot(unique(cotwspe), aes(x = value, y = continent, fill = variable)) + 
  geom_bar(stat = "identity") +
  labs(
    title = "Difference in economic qualities (sectors)",
    subtitle = "depending on the continent",
    x = "Value",
    y = "Continent",
    fill = "Variable"
  )+
  scale_fill_discrete(labels = c("Agriculture", "Industry", "Service"))
```

## Plot and text

```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
Cotw %>%
  mutate(prop_crops_arable = crops/arable) %>%
  ggplot(aes(x = GDP, y = prop_crops_arable, color = continent)) +
  geom_col(alpha = 0.2) +
  theme_minimal() +
  labs(
    title =
  )
  
```
::::
:::

## Different widths

::: columns
:::: {.column width="40%"}
* Some text
* goes here
::::

:::: {.column width="60%"}
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

# Table

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

# To conclude {data-background-image="img/world-map.gif"}

# Thank you for listening :)





